#Matthew Gallagher
#MSiA 400
#Homework 1
---
title: "R Notebook"
output: html_notebook
---
Problem 1
```{r}
my_aov <- function(labels,dataframe){
  
  resp <-c(t(as.matrix(dataframe)))
  k=ncol(dataframe)
  n = nrow(dataframe)
  
  tm <- gl(k,1,n*k,factor(labels))
  
  f_vals <- summary(lm(resp~tm))$fstatistic
  fstat <- qf(.95, f_vals[2], f_vals[3])
  
  if (f_vals[1]>fstat ){
    out = "Reject H0"
  }
  
  else{
    out= "Fail to reject H0"
  }
  
  
return(out)  
}
tensile <- read.table("~/Downloads/Tensile.txt", header=T)
treats <-c("HC5","HC10","HC15","HC20")
my_aov(treats,tensile)

```


Problem 2
a)
```{r}
library(readr)
bostonhousing <- read_delim("~/Downloads/bostonhousing.txt", 
    "\t", escape_double = FALSE, trim_ws = TRUE)


reg <- lm(MEDV~., data=bostonhousing)
summary(reg)

```

INDUS and AGE, you are the weakest link! With the two highest p-values, I am confident these will be the least likely to be in the best model.

b)
```{r}
reg_picked <- lm(MEDV ~ . -AGE -INDUS, data=bostonhousing)
summary(reg_picked)
```


c)
```{r}
sae_f <- sum(abs(summary(reg)$residuals))
sse_f <- sum(I(summary(reg)$residuals^2))
sae_p <- sum(abs(summary(reg_picked)$residuals))
sse_p <- sum(I(summary(reg_picked)$residuals^2))

MAE_f <- sae_f/(506-14)
MSE_f <- sse_f/(506-14)
MAE_p <- sae_p/(506-12)
MSE_p <- sse_p/(506-12)

MAE_f
MSE_f
MAE_p
MSE_p

```

We would choose the model with the smallers MSE and MAE values, which in our case is the reg_picked.

d)
```{r}
reg_step <- stepAIC(reg,direction="both")
summary(reg_step)
```
The model that stepAIC outputs is the same as our reg_picked model!


3)
```{r}
library(readr)
labdata <- read_delim("~/Downloads/labdata.txt", 
    "\t", escape_double = FALSE, trim_ws = TRUE)
```

a)
```{r}
reg3 <- lm(y~., data=labdata)
summary(reg3)
```

```{r}

plot(labdata$x1,labdata$y)
#plot(labdata$x2,labdata$y)
#plot(labdata$x3,labdata$y)
#plot(labdata$x4,labdata$y)
#plot(labdata$x5,labdata$y)
#plot(labdata$x6,labdata$y)
#plot(labdata$x7,labdata$y)
#plot(labdata$x8,labdata$y)

```

From the plots, I believe x1 is most likely to be used in a piecewise regression.

```{r}
m <- mean(labdata$x1)
m
seg.reg3 <- lm(y ~ (x1<m)*x1, data=labdata)
summary(seg.reg3)$adj.r.squared
summary(reg3)$adj.r.squared
```





